Exact Phylodynamic Likelihood\\ via Structured Markov Genealogy Processes

### 2025-07-15 ms.Rnw
fix typo

Code sufficient for the reproduction of all the figures in this paper are freely available for download at \url{https://github.com/kingaa/structured-genealogy-process-paper}.
An archival version of these will be stored on Zotero upon publication of a peer-reviewed version of this paper.
The open-source \pkg{R} package \pkg{phylopomp} (\url{https://github.com/kingaa/phylopomp}) implements the simulation and likelihood-computation algorithms employed here.

>>>>

Codes sufficient for the reproduction of all the figures in this paper are freely available for download at \url{https://github.com/kingaa/structured-genealogy-process-paper}.
An archival version of these will be stored on Zotero upon publication of a peer-reviewed version of this paper.
The open-source \pkg{R} package \pkg{phylopomp} (\url{https://github.com/kingaa/phylopomp}) implements the simulation and likelihood-computation algorithms employed here.
